%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Hui Li} % Your name
% \address{B-1 \\ II , U.P. 208016} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(+1)~608-667-6048 \\ huili98@outlook.com \\ https://huili.tech} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

{\bf University of Wisconsin-La Crosse (La Crosse, WI)} \hfill {\em Sept 2018 - May 2020} 
\\ Master of Software Engineering \hfill {GPA: 3.68/4.00}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\

{\bf South-Central University for Nationalities (Wuhan, China)} \hfill {\em Sept 2015 - June 2018} 
\\ Bachelor of Software Engineering \hfill {GPA: 4.09/5.00}

\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection}{RoloBox}{Sept. 2019 - Apr. 2020}{Mobile Contact Management System with Facial Recognition}{Capstone Project}
\item Agile methodology, Scrum specifically, used in development process.
\item UI designed with Material system and prototyped with Sketch. API design followed with REST paradigm.
\item Use of AWS S3 for image cloud storage, AWS Rekognition for facial analysis. Use of ML kit from Google Firebase for real-time face detection.
\item Web application developed with Angular, mobile client developed with Flutter.
\item Security implementation: Authentication and authorization middleware used in Node.js, XSS and CSRF protection enabled both in client and server side.
\item Keyword: Angular, Node.js, Flutter, MongoDB, AWS, Firebase
\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{WeatherList}{Apr. 2019 - May 2019}{A Web Application that Manage A List of Cities and Their Weather Conditions}{Course Project}
\item Use of a third-party endpoint for providing weather data given a latitude and longitude.
\item Server developed with Spring Boot, use with Thymeleaf template engine for server side rendering.
\item Spring security configuration enabled for user session management and CSRF protection.
\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{TopoNet}{Feb. 2019 - Apr. 2019}{Educational Tool for Demonstrating Network Topology}{Group Project}
\item Use of Angular for front-end, Cytoscape.js for node visualization. Endpoints followed RESTful paradigm.
\item Use of Queue data structure and Promise in JS to prevent callback hell during node animation. Use of Observable interface from RxJS for sibling components interaction in Angular.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{SimpleCart}{Sept. 2018 - Nov. 2018}{A Shopping Software with Cart Support}{Course Project}
\item Use of Bootstrap and JQuery for front-end, Java Servlet and JDBC for backend, MySQL as database.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Academic Presentation
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Presentation}
Hui Li and Kenny Hunt, RoloBox: An Image-Aware Mobile Application using the AWS Ecosystem, The 53rd Annual Midwest Instruction and Computing Symposium(moved online), April 3, 2020.
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages &  JavaScript, Java, HTML5, CSS, Dart \\
Skills \& Framework & Angular, Node.JS/Express, MongoDB, Flutter, Spring Boot \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
% \begin{rSection}{Relevant Courses}
% \itab{\textbf{Core Courses}} \tab{}  \tab{\textbf{Other Courses}}
% \\ \itab{Fluid Mechanics \& its applications } \tab{}  \tab{Computational Methods in Engineering}
% \\ \itab{Thermodynamics} \tab{}  \tab{Fundamental of Computing} 
% \\ \itab{Heat Transfer \& its applications} \tab{}  \tab{Probability and Statistics} 
% \\ \itab{Mass Transfer \& its applications} \tab{} \tab{Calculus \& Linear Algebra}
% \\ \itab{Transport Phenomena (ongoing)} \tab{} \tab{Introduction to Mechanics}
% % \\ \itab{Process Control (ongoing)} \tab{} \tab{Electrodynamics}
% \end{rSection}


\end{document}
